help_extract_from_multiple_netCDFs

### 2018-10-23 src/help_extract_from_multiple_netCDFs.Rmd
link to csv
figuring out formatting...

yyyy_mm_variablename.nc (where variable name can vary in length)

@@

A cut-down version of this .csv is available here XXXX.

>>>>

'yyyy_mm_variablename.nc' (where variable name can vary in length)

@@

A cut-down version of this .csv is available [here](https://drive.google.com/file/d/13ZTZC48o2i0ZktobfukHjaTMh7Qbrfei/view?usp=sharing).
